---
title: "R Notebook"
output: NULL
editor_options: 
  chunk_output_type: inline
---
# Purpose: run all 5 script in one go
## Eventually, include prolific demo data here

# Inputs: 
## Raw qualtrics data
## Prolific demo data
## Loop and merge table 


# Outputs:
## Re-organized data
## Data we will keep and data we will reject
## List of occupations/tasks to hide or continue collection on
##    Sent to Qualtrics and the cloud database
## List of prolific ids and their statuses to update
##    Sent to Prolific
## Final clean and formatted data

# Libraries
```{r}
library(httr)
library(jsonlite)
library(readr)
library(dplyr)
library(googlesheets4)
```

# Make file paths 
```{r}
# Define the base directory
r_dir <- '/Users/adamkuzee/MIT Dropbox/adam/LLM survey/FULL SURVEY/Code and data/Codebases/Deployment codebase/R'

python_dir <- '/Users/adamkuzee/MIT Dropbox/adam/LLM survey/FULL SURVEY/Code and data/Codebases/Deployment codebase/Python'

setwd('/Users/adamkuzee/MIT Dropbox/adam/LLM survey/FULL SURVEY/Code and data/Codebases/Deployment codebase')
```

# Get data from qualtrics and prolific
```{r}
# Define files using file.path() for each step
qualtrics_export_1 <- file.path(python_dir, "Qualtrics API/qualtrics_export.py")

# Get the status of the database
#database_status_1 <- GET(databaseurl.com)
# Check if request was successful
#if (status_code(response) == 200) {
#  # Read CSV directly from response content
#  csv_data <- read_csv(content(response, "text"))
#  print("Data downloaded successfully!")
#  print(head(csv_data))
#} else {
#  stop("Request failed with status code: ", status_code(response))
#}
```

# Clean data and find data to re-collect
```{r}
# Clean Qualtrics data for analyses
cleaning_1 <- file.path(r_dir, "Step 1 - Cleaning raw survey data/full_cleaning_qualtrics_data_14May25_AK.Rmd")

# Identify participants to remove and deny in Prolific
rejection_1 <- file.path(r_dir, "Step 2 - Reject data/full_survey_rejection_15May25_AK.Rmd")
```

# Find remaining tasks and occupations, and updating the lists in Qualtrics and Prolific
```{r}
# Identify the task instances we still need to collect, and which occupations to close entirely
available_tasks_1 <- file.path(r_dir, "Step 3.1 - List task instances & jobs/full_survey_list_tasks_and_occupation_15May25_AK.Rmd")

# Update available occupations 
qualtrics_update_embedded_data_1 <- file.path(python_dir, "Qualtrics API/update_embedded_data.py")

# PUT request to update database - NOT DONE
send_data <- function(data, url, api_key = NULL) {
 cat("Sending", nrow(data), "rows to API...")
 
 # Prepare headers
 headers <- list("Content-Type" = "application/json")
 if (!is.null(api_key)) {
   headers[["Authorization"]] <- paste("Bearer", api_key)
 }
 
 # Send PUT request
 response <- PUT(
   url,
   body = toJSON(data, auto_unbox = TRUE),
   add_headers(.headers = headers),
   timeout(120)
 )
 
 # Check result
 if (status_code(response) %in% c(200, 201, 204)) {
   cat(" Success!\n")
   return(TRUE)
 } else {
   cat(" Failed! Status:", status_code(response), "\n")
   print(content(response, "text"))
   return(FALSE)
 }
}
```

# Update submission statuses in Prolific
```{r}
# Create input document for which statuses to apply
prolific_determine_statuses_1 <- file.path(r_dir, "Step 3.2 - data for appoval + denial in Prolific/full_survey_prolific_statuses_15May25_AK.Rmd")

# Create formatted plan to pass to prolific API
prolific_generate_review_plan_1 <- file.path(python_dir, "Prolific API/Python files/generate_review_plan.py")

# Use prolific API to update submission statuses and pay people
prolific_handle_submissions_1 <- file.path(python_dir, "Prolific API/Python files/execute_prolific_actions.py")
```

# Clean data for sharing
```{r}
# Format the final data as needed for sharing with the team
final_formatting_1 <- file.path(r_dir, "Step 4 - Prepare data for sharing/full_survey_final_data_prep_15May25_AK.Rmd")
```

# Running all scripts
```{r}
# Check if files exist
print(paste("Qualtrics export exists:", file.exists(qualtrics_export_1)))
print(paste("Cleaning script exists:", file.exists(cleaning_1)))
print(paste("Rejection script exists:", file.exists(rejection_1)))
print(paste("Available tasks script exists:", file.exists(available_tasks_1)))
print(paste("Qualtrics update script exists:", file.exists(qualtrics_update_embedded_data_1)))
print(paste("Prolific statuses script exists:", file.exists(prolific_determine_statuses_1)))
print(paste("Prolific review plan script exists:", file.exists(prolific_generate_review_plan_1)))
print(paste("Prolific submissions script exists:", file.exists(prolific_handle_submissions_1)))
print(paste("Final formatting script exists:", file.exists(final_formatting_1)))

# Run all scripts in order
print("Running Qualtrics export")
system(paste("python3", shQuote(qualtrics_export_1)))

print("Running Step 1: Data cleaning")
rmarkdown::render(cleaning_1, quiet = TRUE)

print("Running Step 2: Removing participants")
rmarkdown::render(rejection_1, quiet = TRUE)

print("Running Step 3.1: Listing task instances and occupations")
rmarkdown::render(available_tasks_1, quiet = TRUE)

# Updating available task instances in database - NOT DONE
success <- send_data(your_data, "https://your-api.com/endpoint", "your-key")

# Updating Google Sheet in Prolific
## Getting remaining occupations list
remaining_occupation_list <- read.csv("/Users/adamkuzee/MIT Dropbox/adam/LLM survey/FULL SURVEY/Code and data/FULL SURVEY data/Remaining occupation list/remaining_occupaiton_list.csv")

# Updating Sheet
gs4_auth()  
range_write("1X2nu8GLhDcp5-Z24ytEzt2GbWNeuS7VLw84Owc1OH4M", remaining_occupation_list, sheet = "remaining_occupation_list", range = "A1")

print("Running Qualtrics embedded data update")
system(paste("python3", shQuote(qualtrics_update_embedded_data_1)))

print("Running Step 3.2: Data for approval + denial in Prolific")
rmarkdown::render(prolific_determine_statuses_1, quiet = TRUE)

print("Running Prolific review plan generation")
system(paste("python3", shQuote(prolific_generate_review_plan_1)))

print("Running Prolific submissions handling")
## ONLY RUN THIS WHEN THE REVIEW PLAN HAS BEEN VERIFIED
#system(paste("python3", shQuote(prolific_handle_submissions_1)))

print("Running Step 4: Prepare data for sharing")
rmarkdown::render(final_formatting_1, quiet = TRUE)

print("All scripts completed successfully!")
```


